Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-10 draft/accordionComplexSurfaces.tex
typos

\begin{definition}\label{def: g-vectors for slaloms}
Let~$\alpha$ be a~$\dissection\dual_{\bar Q}$-slalom.
The~$\b{g}$-vector of~$\alpha$ is the vector in~$\R^{Q_0}$ counting the number of times that~$\alpha$ positively crosses each arc of~$\dissection\dual_{\bar Q}$ minus the number of times it crosses each arc negatively.
Here, a crossing is positive when~$\alpha$ leaves a face~$f\dual$ to enter a face~$g\dual$ with the vertex~$f$ being to its right (and thus with~$g$ being to its left).
Otherwise, the crossing is negative.
\end{definition}

>>>>

\begin{definition}\label{def: g-vectors for slaloms}
Let~$\alpha$ be a~$\dissection\dual_{\bar Q}$-slalom.
The~$\b{g}$-vector of~$\alpha$ is the vector in~$\R^{Q_0}$ counting the number of times that~$\alpha$ positively crosses each arc of~$\dissection\dual_{\bar Q}$ minus the number of times it crosses each arc negatively.
Here, a crossing is positive when~$\alpha$ leaves a face~$u\dual$ to enter a face~$v\dual$ with the vertex~$u$ being to its right (and thus with~$v$ being to its left).
Otherwise, the crossing is negative.
\end{definition}
